---
title: "Examples"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BayesPD)
```

## beta_sample_comparison

In Bayesian Analysis, we sometimes need to compare the output of the beta distributions, so this function simplifies the process. All you need to do is supplied the sample size, and parameters for the beta distribution, and it will return the probability that the sample of one distribution is smaller than the other.

There are two groups of parameters required, beta_1 and beta_2. Only one of them can be vectors of length bigger than 1. Since you are comparing the change of one group of parameters to another group of parameters, you can only change one at a time.

```{r, results="hide"}
beta_sample_comparison(sample_size = 9000, beta_a1 = 50:60, beta_b1 = 40:50, beta_a2 = 31, beta_b2 = 21, plot = TRUE)
```

The example shows that we have ten pairs of beta_1, and we want to know how the output of beta_1 compare to the output of beta_2 with beta_1 changing.

## gamma_poisson_ppd

We have two data sets. Assuming those are poisson models, we have gamma prior for the parameter of poisson models.

```{r, results="hide"}
gamma_poisson_ppd(sample_size = 5000, gamma_a1 = 2, gamma_b1 = 1, y1 = c(1,0,0,1,2,2,1,5,2,0,0,0,0,0,0,1,1,1,0,0,0,1,1,2,1,3,2,0,0,3,0,0,0,2,1,0,2,1,0,0,1,3,0,1,1,0,2,0,0,2,2,1,3,0,0,0,1,1), gamma_a2 = 2, gamma_b2 = 1, y2 = c(2,2,1,1,2,2,1,2,1,0,2,1,1,2,0,2,2,0,2,1,0,0,3,6,1,6,4,0,3,2,0,1,0,0,0,3,0,0,0,0,0,1,0,4,2,1,0,0,1,0,3,2,5,0,1,1,2,1,2,1,2,0,0,0,2,1,0,2,0,2,4,1,1,1,2,0,1,1,1,1,0,2,3,2,0,2,1,3,1,3,2,2,3,2,0,0,0,1,0,0,0,1,2,0,3,3,0,1,2,2,2,0,6,0,0,0,2,0,1,1,1,3,3,2,1,1,0,1,0,0,2,0,2,0,1,0,2,0,0,2,2,4,1,2,3,2,0,0,0,1,0,0,1,5,2,1,3,2,0,2,1,1,3,0,5,0,0,2,4,3,4,0,0,0,0,0,0,2,2,0,0,2,0,0,1,1,0,2,1,3,3,2,2,0,0,2,3,2,4,3,3,4,0,3,0,1,0,1,2,3,4,1,2,6,2,1,2,2), confidence_interval = c(0.025, 0.975), using_MCMC = FALSE, poisson_fitting_mean = 1.4)
```

Here the example shows that we have two data sets: y1 and y2. given priors for poisson models. Setting using MCMC to false indicates that we want to derive the posterior distribution, which is Negative Binomial distribution. The first two graphs show the sampling from posterior predictive distribution. Given poisson_fitting_mean, the red line is the density of poisson distribution, and the black line is the emprical distribution of the data, so we can check if they match, then if poisson model with given poisson_fitting_mean is proper. If the confidence interval is given, there will be two variables in the output: theta2_minus_theta1_quantile and y_tidle2_minus_ytilde1_quantile. As the variable names show, they are the interval that theta2-theta1 lies in and interval that y_tilde2-y_tilde1 lies in.

Since we have sample_size theta2_posterior, then for each of them, we can sample 218 data to see if it matches the real data. One way to check is to see the number of 0 and number of 1, and draw the sample_size number of points in one figure then check the number of 0 and number of 1 in the original data.

```{r, results="hide"}
normal_gamma_conjugate_family(sample_size = 10000, mu_0 = 5, sigma_0_sequare = 4, kappa_0 = 1, nu_0 = 2, y.1 = c(2.11,9.75,13.88,11.3,8.93,15.66,16.38,4.54,8.86,11.94,12.47,11.11,11.65,14.53,9.61,7.38,3.34,9.06,9.45,5.98,7.44,8.5,1.55,11.45,9.73), y.2 = c(0.29,1.13,6.52,11.72,6.54,5.63,14.59,11.74,9.12,9.43,10.64,12.28,9.5,0.63,15.35,5.31,8.49,3.04,3.77,6.22,2.14,6.58,1.11), y.3 = c(4.33,7.77,4.15,5.64,7.69,5.04,10.01,13.43,13.63,9.9,5.72,5.16,4.33,12.9,11.27,6.05,0.95,6.02,12.22,12.85), confidence_interval = c(0.025, 0.975))
```
